Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-09-23 paper.tex
Updated Experimental Setup
Work in progress.

@@

@@

@@

As a proof-of-concept, we implemented the algorithm with Docker containers by
solving the OneMax problem to compare it with a traditional GA algorithm using
the DEAP (Distributed Evolutionary Algorithms in Python) library
\cite{fortin2012deap}. The OneMax problem \cite{krejca2020lower,witt2019upper}
uses a genetic algorithm to evolve a population of randomly generated
individuals with zeros and ones, and it stops until a solution of only ones is
found.

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig5_processes_containers.pdf}
    \caption{Life-Cycle algorithm processes in containers comparison.} \label{fig.processes_containers}
    \end{figure}

One strategic difference in our algorithm implementation is the reproduction
process, which is flexible to work in parallel with multiple couple selection
methods, for example, tournament selection, random selection (Closed
Reproduction process), and couple match by creating a new mating individual
(Open Reproduction process). We use many combinations of the containerized
processes, up to the minimum number required to obtain good results.
Figure~\ref{fig.processes_containers} shows a comparison of only two alternatives for the
implementation of the algorithm. Our experimentation started with a
configuration of ten processes and ended in five, shown on the left and right
sides of Fig.~\ref{fig.processes_containers}, respectively.

@@

In our four experiments, we needed to match or balance the experimentation
parameters according to the specifications of the algorithm used by the DEAP
library. This is to be able to verify if our algorithm would also converge on
the solutions in a similar number of evaluations and execution time.
Table~\ref{tab.configuration} shows the OneMax initial configuration for DEAP and Life-Cycle
experiment.

\begin{table}[]
    \centering        
    \caption{OneMax initial configuration for DEAP and Life-Cycle experiment.}\label{tab.configuration}
    \begin{tabular}{|l|l|l|}
    \hline
    \textbf{Configuration} & \textbf{DEAP} & \textbf{Life-Cycle} \\ \hline
    Population & 60 & 60 \\ \hline
    Max Generation & 20 & 20 \\ \hline
    Stagnation & Off & 10 \\ \hline
    Chromosome Length & 20 & 20 \\ \hline
    Target Fitness & 20 & 20 \\ \hline
    Crossover Rate & 100 & 100 \\ \hline
    Mutation Rate & 7 & 7 \\ \hline
    Tournament Rate & 100 & 50 \\ \hline
    Tournament Sample & 3 & 4 \\ \hline
    Open Reproduction Rate & NA & 5 \\ \hline
    Closed Reproduction Rate & NA & 45 \\ \hline
    Max Age & NA & 80 \\ \hline
    Base Approval & NA & 80 \\ \hline
    Goal Approval & NA & 100 \\ \hline
    \end{tabular}
    \end{table}

@@

Where:
\begin{itemize}
    \item[]	    F is the gravitational force acting between two objects.
    \item[]	    m1 and m2 are the masses of the objects.
    \item[]	    r is the distance between the centers of their masses.
    \item[]	    G is the gravitational constant: 6.67430(15)×10−11 m3⋅kg−1⋅s−2.
\end{itemize}

>>>>

\usepackage{booktabs}       %Booktabs Table Style

@@

The following tables show the configuration used to execute the experiments for
the analysis and comparison in this paper. In
Table~\ref{tab.general_configuration}, we can find the General Configuration
for the Animal Life Cycle Algorithm. All values from this configuration
remained constant during all phases of the experiment runs. The following
table, Table~\ref{tab.benchmark_fun_config}, shows the values used for the
Classic Benchmark Functions for Optimization, where these are adjusted
accordingly for each function.

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
% To change the size of the font use \scriptsize or \tiny
\begin{table}[]
    \scriptsize
    \centering        
    \caption{Animal Life Cycle Algorithm (ALCA) General Configuration.}\label{tab.general_configuration}
    \begin{tabular}{@{}ll@{}}
    \toprule
    \multicolumn{2}{l}{ALCA General Configuration} \\ \midrule
    Function name & ALL \\
    Population & 500 \\
    Target error & 1.00E-08 \\
    Crossover rate & 100 \\
    Mutation rate & 7 \\
    Max age & 40 \\
    Tournament rep. & 100 \\
    Sample size & 20 \\
    Base approval & 80 \\
    Goal approval & 200 \\ \bottomrule
    \end{tabular}
    \end{table}

\begin{table}[]
    \scriptsize
    \centering        
    \caption{Classic Benchmark Functions for Optimization Configuration.}\label{tab.benchmark_fun_config}
    \begin{tabular}{@{}llllllll@{}}
    \toprule
    \multicolumn{8}{l}{Benchmark Configuration Setup} \\ \midrule
    Function name & Ackley & Bohachevsky & Griewank & Rastrigin & Sphere & Rosenbrock & Rosenbrock \\
    Dimensions & 5, 10 & 5, 10 & 5, 10 & 5, 10 & 5, 10 & 5 & 10 \\
    Max evaluations & 200,000 & 200,000 & 200,000 & 200,000 & 200,000 & 500,000 & 1,000,000 \\
    Max stagnation & 50,000 & 50,000 & 50,000 & 50,000 & 50,000 & 125,000 & 250,000 \\
    Target fitness & -20.0 & -12.0 & -150.0 & -80.0 & -50.0 & -3500.0 & -3500.0 \\
    Bound matrix & {[}-32, 32{]} & {[}-2, 2{]} & {[}-500, 500{]} & {[}-5, 5{]} & {[}-5, 5{]} & {[}-2, 2{]} & {[}-2, 2{]} \\ \bottomrule
    \end{tabular}
    \end{table}

@@

%One strategic difference in our algorithm implementation is the reproduction process, which is flexible to work in parallel with multiple couple selection methods, for example, tournament selection, random selection (Closed Reproduction process), and couple match by creating a new mating individual (Open Reproduction process). We use many combinations of the containerized processes, up to the minimum number required to obtain good results. Figure~\ref{fig.processes_containers} shows a comparison of only two alternatives for the implementation of the algorithm. Our experimentation started with a configuration of ten processes and ended in five, shown on the left and right sides of Fig.~\ref{fig.processes_containers}, respectively.
%In our four experiments, we needed to match or balance the experimentation parameters according to the specifications of the algorithm used by the DEAP library. This is to be able to verify if our algorithm would also converge on the solutions in a similar number of evaluations and execution time. Table~\ref{tab.configuration} shows the OneMax initial configuration for DEAP and Life-Cycle experiment.

@@

@@

@@
